Low Complexity Adaptive Beamformer\\ for Active Sonar Imaging

### 2015-10-01 LCAforActiveSonarImaging/lca.tex
la2pdf commit - 2015:10:01	15:44:40	(Thu 1.Oct)

% NOTE: PDF hyperlink and bookmark features are not required in IEEE
%       papers and their use requires extra complexity and work.
% \newcommand\MYhyperrefoptions{bookmarks=true,bookmarksnumbered=true,
% pdfpagemode={UseOutlines},plainpages=false,pdfpagelabels=true,
% colorlinks=true,linkcolor={black},citecolor={black},urlcolor={black},
% pdftitle={Optimal Window Design for the Low Complexity Adaptive Beamformer in Active Sonar Imaging},
% pdfsubject={},
% pdfauthor={Jo Inge Buskenes},
% pdfkeywords={adaptive beamforming, beamforming, complexity, sonar, active}}%
\ifCLASSINFOpdf
%    \usepackage[\MYhyperrefoptions,pdftex]{hyperref}
   \usepackage[pdftex,
    final,                %Keep hyperlink stuff even when in draft mode
    breaklinks=true,      %Break links when necessary
    linktocpage=true,     %Enable link to page?
    linkcolor=black,  %Colour of links to labels within document
    citecolor=black,      %Colour of links to the biliography
    filecolor=red,        %Colour of links to local files
    pagecolor=black,        %Colour of links to other pages withing document
    urlcolor=Blue,        %Colour of the links to external URLs
    colorlinks=true,      %??
    plainpages=false,     %Store roman/arabic numbering differently to avoid
    bookmarksnumbered ]{hyperref}
\else
   \usepackage[\MYhyperrefoptions,breaklinks=true,dvips]{hyperref}
   \usepackage{breakurl}                        % Allows 'dvips' driver to break links
\fi

@@

Now let $a=\a_\phi\T\x$ and $b=\b_\phi\T\x$. The beamformer output can then be written as:
%
\begin{align}
|\w\H\x|^2 &= \Big| \alpha a - (1-\alpha)b \Big|^2 \nn
&= \alpha^2 (aa^* + ab^* + a^*b + bb^*) \nn
&- \alpha(ab^* + a^*b + 2bb^*) + bb^*
\end{align}
%
This is a convex function with a single minimum, which we find by differentiating with respect to $\alpha$ and setting equal to 0:
%
\begin{align}
\frac{\partial}{\partial\alpha} |\w\H\x|^2 
&= 2\alpha (aa^* + ab^* + a^*b + bb^*) \nn
&- (ab^* + a^*b + 2bb^*) = 0,
\end{align}
%
which has the solution:
%
\begin{align}
\alpha &= \frac{ab^* + a^*b + 2bb^*}{2(aa^* + ab^* + a^*b + bb^*)}.
\end{align}
%
In this computation there are only 4 and 7 unique complex additions and multiplications, respectively. If we used this to analytically solve for $\alpha$, but perform the search for $\phi$, the computational complexity of LCA would be of O($11MN_\phi)$ instead of O($MN_\alpha N_\phi)$. The value for $\alpha$ would also be the optimal in the minimum variance sense.

@@

\bibliographystyle{IEEEtran}
\bibliography{references}
% 
% 
\input{bio/jo_inge_buskenes}
\input{bio/andreas_austeng}

>>>>

% NOTE: PDF hyperlink and bookmark features are not required in IEEE
%       papers and their use requires extra complexity and work.
% \newcommand\MYhyperrefoptions{bookmarks=true,bookmarksnumbered=true,
% pdfpagemode={UseOutlines},plainpages=false,pdfpagelabels=true,
% colorlinks=true,linkcolor={black},citecolor={black},urlcolor={black},
% pdftitle={Optimal Window Design for the Low Complexity Adaptive Beamformer in Active Sonar Imaging},
% pdfsubject={},
% pdfauthor={Jo Inge Buskenes},
% pdfkeywords={adaptive beamforming, beamforming, complexity, sonar, active}}%
\ifCLASSINFOpdf
%    \usepackage[\MYhyperrefoptions,pdftex]{hyperref}
   \usepackage[pdftex,
    final,                %Keep hyperlink stuff even when in draft mode
    breaklinks=true,      %Break links when necessary
    linktocpage=true,     %Enable link to page?
    linkcolor=black,  %Colour of links to labels within document
    citecolor=black,      %Colour of links to the biliography
    filecolor=red,        %Colour of links to local files
    pagecolor=black,        %Colour of links to other pages withing document
    urlcolor=Blue,        %Colour of the links to external URLs
    colorlinks=true,      %??
    plainpages=false,     %Store roman/arabic numbering differently to avoid
    bookmarksnumbered ]{hyperref}

\else
   \usepackage[\MYhyperrefoptions,breaklinks=true,dvips]{hyperref}
   \usepackage{breakurl}                        % Allows 'dvips' driver to break links
\fi

@@

Now let $a=\a_\phi\T\x$ and $b=\b_\phi\T\x$. The beamformer output can then be written as:
%
\begin{align}
|\w\H\x|^2 &= \Big| \alpha a - (1-\alpha)b \Big|^2 \nn
&= \alpha^2 (aa^* + ab^* + a^*b + bb^*) \nn
&- \alpha(ab^* + a^*b + 2bb^*) + bb^*
\end{align}
%
This is a convex function with a single minimum, which we find by differentiating with respect to $\alpha$ and setting equal to 0:
%
\begin{align}
\frac{\partial}{\partial\alpha} |\w\H\x|^2 
&= 2\alpha (aa^* + ab^* + a^*b + bb^*) \nn
&- (ab^* + a^*b + 2bb^*) = 0,
\end{align}
%
which has the solution:
%
\begin{align}
\alpha &= \frac{ab^* + a^*b + 2bb^*}{2(aa^* + ab^* + a^*b + bb^*)}.
\end{align}
%
In this computation there are only 4 and 7 unique complex additions and multiplications, respectively. If we used this to analytically solve for $\alpha$, but perform the search for $\phi$, the computational complexity of LCA would be of O($MN_\phi)$ instead of O($MN_\alpha N_\phi)$. The solution for $\alpha$ would also yield the optimal beamformer output in the minimum variance sense.

@@

\bibliographystyle{IEEEtran}
\bibliography{references}
% 
% 
\input{bio/jo_inge_buskenes}
\input{bio/roy_edgar_hansen}
\input{bio/andreas_austeng}
